---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# sysreqs

The goal of sysreqs is to make it easy to identify R package system dependencies. There are two components to this package: an "API" and a wrapper package. 

This API and package is based on [`rstudio/r-system-requirements`](https://github.com/rstudio/r-system-requirements) and the API client for [RStudio Package Manager](https://www.rstudio.com/products/package-manager/). The functionality is inspired by [`pak::pkg_system_requirements()`]. 

## Installation

This package can be installed from github.

```r
remotes::install_github("josiahparry/r-sysreqs")
```

## Usage

The primary function is `get_pkg_sysreqs()` this will return a named list for each system dependency identified where each element is a named list for each required system library containing the dependencies, recommended pre-installation and post-installation commands. This function works for only one package at a time.

```{r}
library(sysreqs)

get_pkg_sysreqs("igraph", os = "ubuntu", "16.04")
```

If you seek the dependencies for multiple packages use `get_pkgs_sysreqs()`. 

```{r}
get_pkgs_sysreqs(
  c("rJava", "igraph", "rgdal", "spdep"),
  "ubuntu", "16.04"
)
```

Additionally, if you want to retrieve the json simply parses as a list without any helpers, please use the various `fetch_*()` functions.

- `fetch_systems()`: supported operating systems
- `fetch_patterns()`: the regex patterns to identify system dependencies
- `fetch_pkg()`: returns package information (name, version, and system requirements as written in the DESCRIPTION
- `fetch_rules()`: returns the rules for a given system library
- `fetch_pkg_deps()`: returns the matched system dependencies

## The API

Access to the R system dependency data that are available from [`rstudio/r-system-requirements`](https://github.com/rstudio/r-system-requirements) is made available by a simple plain-text website hosted at [`r-sysdeps.josiahparry.com`](https://r-sysdeps.josiahparry.com). The sysreq package makes calls to that url to fetch information

Contents: 

- [`patterns`](patterns.json) is used as a look-up table for identify system dependencies
- [`systems`](systems.json) provides a list of available operating systems (limited to linux distributions)
- [`/rules`](rules/index.html) is a directory containing the lookup rools for each system dependencies requirements e.g. `rules/gdal.json`
- [`/pkgs`](pkgs/index.html) is a directory containing json files for each package listing their name, version, and system dependencies e.g. `pkgs/igraph.json`


