---
title: "API Reference"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{API Reference}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = FALSE
)
```

The "API" is a simple based plain text website based on json files. These json files can be retrieved via `GET` requests and as such behave much like an API.

## The root

```{r echo = FALSE}
library(reactable)

all_fps <- data.frame(filepath = list.files(here::here("_api"),
                                            recursive = TRUE))

fps_clean <- all_fps |> 
  dplyr::filter(!grepl("index.html", filepath)) |> 
  dplyr::mutate(
    filepath = fs::path("", filepath),
    Section = dplyr::case_when(
    grepl("^/pkgs/", filepath) ~ "/pkgs",
    grepl("^/rules/", filepath) ~ "/rules",
    TRUE ~ ""
    ),
    name = sub(".json$", "", basename(filepath)),
    Letter = ifelse(Section != "", toupper(substr(name, 1, 1)), ""))
```


```{r}
root_fps <- fps_clean |> 
  dplyr::filter(Section == "") 

root_fps |>   
  reactable(
  #  groupBy = c("Section", "Letter"),
    columns = list(
      name = colDef(cell = function(value, index) {
        htmltools::tags$a(href = root_fps$filepath[index],
                          target = "_blank",
                          value)
      },
      name = "Name"
    ),
    filepath = colDef(show = FALSE),
    Letter = colDef(name = "A-z", show = FALSE, maxWidth = 25),
    Section = colDef(show = FALSE)
  ),
   resizable = TRUE, wrap = FALSE, bordered = TRUE,
  defaultColDef = colDef(minWidth = 50)
)
```

### Patterns 

`patterns.json` contains the regex patterns used to match the `SystemRequirements` field in a `DESCRIPTION` file to the correct system requirement. It looks like 

```json
{
    "apparmor": [
        "\\bapparmor\\b",
        "\\blibapparmor\\b"
    ],
    "atk": [
        "\\batk\\b"
    ]
...
..
. 
```

### Systems 


`systems.json` enumerates the supported operating systems. 


```
    {
        "os": [
            "linux"
        ],
        "distribution": [
            "ubuntu"
        ],
        "versions": [
            ["14.04"],
            ["16.04"],
            ["18.04"],
            ["20.04"]
        ]
    }
...
..
.
``` 


<br> 

## Packages & System Requirement Rules

The two other paths are `/pkgs` and `/rules`.

- `/pkgs`
  - contains the package name, recorded version, and system requirements as recorded in the DESCRIPTION for all packages in the CRAN package database that have system requirements. 
  - it is formatted like `/pkgs/{pkg-name}.json`
- `/rules`
  - contains system library regex matching patterns and operating system constraints--e.g. system dependencies and recommended pre & post installation steps. 
  - it is formatted like `/pkgs/{sys-lib-name}.json`.
  

```{r}  
pkg_rules_fps <- fps_clean |> 
  dplyr::filter(Section != "") 

pkg_rules_fps |> 
  reactable(
    groupBy = c("Section", "Letter"),
    columns = list(
      name = colDef(cell = function(value, index) {
        htmltools::tags$a(href = pkg_rules_fps$filepath[index],
                          target = "_blank",
                          value)
      },
      name = "Name"
    ),
    filepath = colDef(show = FALSE),
    Letter = colDef(name = "A-z", maxWidth = 85),
    Section = colDef(maxWidth = 145)
  ),
  resizable = TRUE, wrap = FALSE, bordered = TRUE,
  defaultColDef = colDef(minWidth = 50)
)
```


### Example package json file

```json
[{"Package":"dbscan","Version":"1.1-10","SystemRequirements":"C++11"}]

```


### Example rules json file


```json
{
  "patterns": ["\\bhdf5\\b", "\\blibhdf5\\b"],
  "dependencies": [
    {
      "packages": ["libhdf5-dev"],
      "constraints": [
        {
          "os": "linux",
          "distribution": "ubuntu"
        },
        {
          "os": "linux",
          "distribution": "debian"
        }
      ]
    },
    {
      "packages": ["hdf5-devel"],
      "pre_install": [
        {
          "command": "yum install -y epel-release"
        }
      ],
      "constraints": [
        {
          "os": "linux",
          "distribution": "centos",
          "versions": ["6", "7"]
        }
      ]
    },
    {
      "packages": ["hdf5-devel"],
      "pre_install": [
        {
          "command": "dnf install -y epel-release"
        }
      ],
      "constraints": [
        {
          "os": "linux",
          "distribution": "centos",
          "versions": ["8"]
        }
      ]
    },
    {
      "packages": ["hdf5-devel"],
      "pre_install": [
        {
          "command": "rpm -q epel-release || yum install -y https://dl.fedoraproject.org/pub/epel/epel-release-latest-6.noarch.rpm"
        }
      ],
      "constraints": [
        {
          "os": "linux",
          "distribution": "redhat",
          "versions": ["6"]
        }
      ]
    },
    {
      "packages": ["hdf5-devel"],
      "pre_install": [
        {
          "command": "rpm -q epel-release || yum install -y https://dl.fedoraproject.org/pub/epel/epel-release-latest-7.noarch.rpm"
        }
      ],
      "constraints": [
        {
          "os": "linux",
          "distribution": "redhat",
          "versions": ["7"]
        }
      ]
    },
    {
      "packages": ["hdf5-devel"],
      "pre_install": [
        {
          "command": "dnf install -y https://dl.fedoraproject.org/pub/epel/epel-release-latest-8.noarch.rpm"
        }
      ],
      "constraints": [
        {
          "os": "linux",
          "distribution": "redhat",
          "versions": ["8"]
        }
      ]
    },
    {
      "packages": ["hdf5-devel"],
      "constraints": [
        {
          "os": "linux",
          "distribution": "opensuse"
        },
        {
          "os": "linux",
          "distribution": "sle",
          "versions": ["12.3"]
        }
      ]
    },
    {
      "packages": [
        "mingw-w64-x86_64-hdf5",
        "mingw-w64-i686-hdf5"
      ],
      "constraints": [
        {
          "os": "windows"
        }
      ]
    }
  ]
}
```
